%-------------------------
% Resume in Latex
% Author : DAIR Office
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

%Setup hyperref package, and colours for links
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

%for social icons
\usepackage{fontawesome5}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{:\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}, \hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
% \vspace{0.5mm}
\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.4mm}
\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Sarthak Mishra} % Your Name
\newcommand{\course}{BS-MS in Physics} % Your Course
% \newcommand{\roll}{18388} % Your Roll No.
\newcommand{\phone}{7077965840} % Your Phone Number
\newcommand{\emaila}{sarthakmishrachess@gmail.com} %Email 1
\newcommand{\emailb}{sarthak18@iiserb.ac.in} %Email 2
\newcommand{\github}{Nusart} %Github
\newcommand{\twitter}{nusart829} %Twitter
\newcommand{\linkedin}{nusart829} %linkedin




\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge \textbf{\name} \\[7.5pt]
\href{https://github.com/Nusart}{\raisebox{-0.05\height}\faGithub\ Nusart} \ $|$ \ 
\href{https://linkedin.com/in/nusart829}{\raisebox{-0.05\height}\faLinkedin\ nusart829} \ $|$ \ 
% \href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
\href{mailto:sarthakmishrachess@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ sarthakmishrachess@gmail.com} \ $|$ \ 
\href{tel:+91-7077965840}{\raisebox{-0.05\height}\faMobile \ +91-7077965840} \\
\end{tabularx}


%----------EDUCATION-----------------
\section{Education}
\setlength{\tabcolsep}{5pt} % Default value: 6pt
\resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Science Education and Research Bhopal}{CPI: 8.19/10}
      {\small Integrated Bachelors of Science - Masters of Science}{2018 - 2023 (Expected)}
      % \vspace{3mm} 
      \hspace{1.5mm}{\small \textit{Major in \textbf{Physics}, Minor in \textbf{Data Science and Engineering}}}
	    
    \resumeSubheading
      {Senior Secondary Education}{Percentage: 93\%}
      {\small Class 12th (CBSE board)}{2015 - 2017}
      % \vspace{3mm} 
      \hspace{1.5mm}{\small \textit{Major subjects: Physics, Chemistry, Maths, Biology}}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ongoing Master's Thesis}{University of Porto, Portugal}
      {Underwater Systems and Technology Laboratory (LSTS) in collaboration with Moon Lab}{Aug 2022 - Apr 2023}
      \vspace{-1mm}
      \resumeItemListStart
        \item {Trajectory optimization for a 6 Degree of Freedom (DOF) Autonomous Underwater Vehicle (AUV) using Model Predictive Control (MPC).}
            \subitem {Development of an optimal trajectory of a 6DOF underwater vehicle interacting with time varying ocean flow fields with the use of a pre-defined cost function in MPC and then using a deep learning model to predict the best suitable cost function for the MPC.}
            \textnormal{\href{https://github.com/Nusart/ms-thesis/blob/main/18388_Sarthak_report.pdf}{[Synopsis]}}
      \resumeItemListEnd   
      
    \resumeSubheading
    {Moon Lab}{IISER Bhopal}
      {Summer Internship (collaboration with LSTS Porto)}{May - July 2022}
      \vspace{-1mm}
      \resumeItemListStart
        \item {Autonaut speed prediction and trajectory optimization using wave data from forecast models.}
            \subitem {Development of a machine learning model to predict the speed and trajectory of an Autonaut Unmanned Surface Vehicle with the help of datasets of the missions carried out in open oceans (Irish-Atlantic Region) and Fjords (near Norway).}
        \resumeItemListEnd
    
    % \resumeSubheading
    %   {Dr. Ritam Mallik, Dept. of Physics}{IISER Bhopal}
    %   {Online Summer Internship}{May - July 2020}
    %   \vspace{-1mm}
    %   \resumeItemListStart
    %     \item {Galaxy image classification using Regression and Ensemble models.}
    %         \subitem {Image Analysis on Galaxy Images (GAMA catalogue) and classification using Local Weighted Regression and Ensemble Learning.}
    %     \resumeItemListEnd
    
    \resumeSubheading
      {Coral Lab}{IIIT Delhi}
      {Winter and Summer Internship}{Dec 2018, May - July 2019}
      \vspace{-1mm}
      \resumeItemListStart
        \item Obstacle avoidance using Turtlebot.
        \subitem {Learning Robot Operating System (ROS) framework and applying obstacle avoidance algorithms on Turtlebot to navigate through a closed environment.}
      \resumeItemListEnd      
  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------------
\section{Publications}
 \resumeSubHeadingListStart
 \resumePOR{Sarthak Mishra} % Award
    {Renato Mendes, Joao Sousa, Alberto Dallolio, Sujit P B, "Autonaut Speed Modelling for \\Real-time Motion Planning in Irish-Atlantic ocean", IEEE/MTS OCEANS 2023 conference, Limerick, Ireland.\\{\textit{(Accepted)}}} % Event
    {} %Event Year 
 \resumeSubHeadingListEnd


%-----------SKILLS-----------------
\section{Technical Skills}
 \resumeHeadingSkillStart
  \resumeSubItem{Programming/scripting languages} % Category
    {Python*, C/C++, \LaTeX, HTML, CSS, Javascript, PHP, MySQL.}
  \resumeSubItem{Libraries/Frameworks/Simulators} % Category
    {ROS/ROS2, Gazebo,  \href{https://uuvsimulator.github.io/}{UUV Simulator}*,
    Pandas*, Numpy, Matplotlib*, Keras, Tensorflow, Pytorch, Git, MATLAB, Wolfram Mathematica, Qutip.} % Skills
  \resumeSubItem{Operating Systems}
    {Windows, Linux*.} 
 \resumeSubItem{Soft Skills} % Category
    {English, Hindi, Odia, Sanskrit, Spanish.} \hfill \textit{\footnotesize{*Proficient}} 
 \resumeHeadingSkillEnd

% \vspace{1em}
%-----------CONFERENCES-----------------
\section{Conferences, Symposiums and Workshops}    
 \resumeSubHeadingListStart  
    \resumePOR{Conference presentation} % Award
    {Accepted for technical paper presentation on "Real-time Motion \\ Planning in Irish-Atlantic ocean" at \textbf{IEEE/MTS OCEANS 2023 conference} at University of \\ Limerick, Ireland.} % Event
    {Jun 2023} %Event Year
    
    \resumePOR{IITB CSE Research Symposium} % Award
    {Selected to attend this 2 day symposium to showcase the \\cutting-edge research in the field of \textbf{AI/ML}, computer systems, and theoretical CS.} % Event
    {Mar 2023} %Event Year
    
    \resumePOR{Soft skills and Career Development workshop \href{https://drive.google.com/file/d/1QU1xaKHtkA27EPc2FdgE4_J931uG89aO/view?usp=sharing}{\footnotesize \faIcon{link}}} % Award
    {a 2.5 day intensive workshop on \\ behavioral skills and personality development organised by ICDPC, IISER Bhopal.} % Event
    {Mar 2023} %Event Year
    
    \resumePOR{WSDM 2023} % Award
    {Recieved the \textbf{ACM SIGWEB Fair Access Student Participation Award} for \\ participation in the \textbf{16th ACM International Conference on Web Search and Data Mining} \\ organised by National University of Singapore.} % Event
    {Feb - Mar 2023} %Event Year
    
    \resumePOR{17th Academic Research and Careers for Students Symposium} % Award
    {\textnormal{co-located with} \\ \textbf{ACM India Annual Event} organised by ACM India at OIST Bhopal.} % Event
    {Feb 2023} %Event Year

    % \resumePOR{\textnormal{Workshop on} Internet of Things (IoT) using Raspberry Pi \href{https://drive.google.com/file/d/129PuM3DhWDg-LBX_gbeQowdb0A1R9MFN/view?usp=sharing}{\footnotesize  \faIcon{link}}} % Award
    % {organised by Technex’20 fest \\ IIT-BHU Varanasi.} % Event
    % {Aug 2019} %Event Year

    % \resumePOR{\textnormal{Workshop on} Science Writing \href{https://drive.google.com/file/d/1K6YHh-JJ27R-Fujma4Svp2wgDMyxi3H9/view?usp=sharing}{\footnotesize  \faIcon{link}}} % Award
    % {a two day training on Science writing and blogging organised \\ by Science Media Center at IISER Pune.} % Event
    % {May 2019} %Event Year
 \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProject
      {Monte carlo localization simulation of Mobile Robots}
      {}     {\textnormal{\href{https://github.com/Nusart/monte-carlo-localization}{\Large \faGithub}}}{}
      \vspace{-5.5mm}
      \resumeItemListStart
        \item {Learning about Monte Carlo Localization algorithm through the paper- Monte Carlo localization of Mobile Robots by Frank Dellaert et. al. by creating simulations based on the paper.}
    \resumeItemListEnd

    \resumeProject
      {Synthetic Satellite Image generation using Generative Adversarial Networks (GANs)}{}      {\textnormal{\href{https://github.com/Nusart/synthetic-satellite-imagery-GANs}{\Large \faGithub}}}{} %Website
      \vspace{-5.5mm}
      \resumeItemListStart
        \item {Image style transfer using GANs on multi-spectral images to generate and translate a masked layer to output high quality synthetic images.}
        % \item {Project Work Done 2}
    \resumeItemListEnd
    % \newpage
    \resumeProject
      {Drug Discovery on chEMBL dataset}{}      {\textnormal{\href{https://github.com/Nusart/drug-discovery-chembl}{\Large \faGithub}}}{}
      \vspace{-5.5mm}
      \resumeItemListStart
        \item {Traditional Machine Learning based model to predict the concentration of a drug that is required for 50\% inhibition (IC50) in vitro for various drugs manually curated by chEMBL database to fight SARS CoV-2.}
    \resumeItemListEnd

    % \resumeProject
    %   {Couzins Model}
    %   {}     {\textnormal{\href{https://github.com/Nusart/Couzins-model}{\large \faGithub}}}{}
    %   \vspace{-5.5mm}
    %   \resumeItemListStart
    %     \item {A simulation of the Couzins Model to study the collective animal behaviour.}
    % \resumeItemListEnd
    
    \resumeProject
      {Question Answering from e-manual using word embeddings in Natural Language Processing}{}    {\textnormal{\href{https://github.com/Nusart/question-answering-NLP}{\Large \faGithub}}}{}
      \vspace{-5.5mm}
      \resumeItemListStart
        \item {Finding the most relevant question text corpus of user query from e-manual faqs and thus finding their corresponding answers.}
    \resumeItemListEnd
    
    \resumeProject
      {Multi-class music Genre classification using Machine Learning}
      {}     {\textnormal{\href{https://github.com/Nusart/music-genre-classification}{\Large \faGithub}}}{}
      \vspace{-5.5mm}
      \resumeItemListStart
        \item {Given a raw unprocessed dataset of multiple audio files, classify each file into respective music genres such as Jazz, Hip-hop, Disco, Blues, etc with the help of tuned ML models.}
    \resumeItemListEnd
    
    % \resumeProject
    %   {Spin to Spring mapping of a two-level Quantum System}
    %   {}      {\textnormal{\href{https://github.com/Nusart/spin-to-spring-mapping-of-two-level-quantum-system}{\large \faGithub}}}{}
    %   \vspace{-5.5mm}
    %   \resumeItemListStart
    %     \item {Study of the behavior of the Spin Magnetization Vector through simulation of a nucleus subjected to a constant magnetic field on the application of Radio Frequency Pulse.}
    % \resumeItemListEnd
    
    % \resumeProject
    %   {Web development}{}      {\textnormal{\href{https://github.com/Nusart/cicada}{\large \faGithub}}}{}
    %   \vspace{-5.5mm}
    %   \resumeItemListStart
    %     \item {Cicada `21, `20}
    %     \subitem {Creator of an online treasure hunt game inspired by the famous `CICADA 3301 Online Treasure' that requires extensive internet browsing and the use of browser developer tools to navigate through various pages on the internet.}
    %     \item {Chrysalis Science Magazine}
    %     \subitem {Owner and maintainer of e-blog for institute science magazine.}
    %     % {\href {https://students.iiserb.ac.in/chrysalis/}{Website}}
    % \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------COURSES-----------------
\section{Key courses taken}
\resumeHeadingSkillStart
\resumeSubItem{Mathematics, Physics and Computer Science} % Category
    {Linear Algebra, Multivariable Calculus, Probability \& Statistics, Mathematical Methods, Computational Physics, Numerical Methods and Programming, Physics through Computational Thinking, \textbf{Deep Learning}, \textbf{Data science and Machine Learning}, \textbf{Artificial Intelligence}, Advanced Programming in Python, AI and it's scientific application.}
\resumeSubItem{e-Certificate courses} % Category
    {Satellite Photogrammetry and its Application (Indian Institute of Remote Sensing, IIRS Dehradun) \href{https://drive.google.com/file/d/1Va-hpY1TD7TdQ1_NzGwa9ggJ51vc5G4F/view?usp=share_link}{\footnotesize  \faIcon{link}}, Basics of Machine Learning (IISERB) \href{https://drive.google.com/file/d/1BFrfINnnO-heBwsiXnqa4u2_QSWYoIO0/view?usp=share_link}{\footnotesize  \faIcon{link}}, Computer Vision Basics using MATLAB (Coursera) \href{https://drive.google.com/file/d/1puteJJLp2zHHtByPVuY3wXHVIiDmp87M/view?usp=sharing}{\footnotesize \faIcon{link}}, MATLAB onramp (Mathworks) \href{https://drive.google.com/file/d/1-HQdhUhWTQ7qmyNNIMeb9y5ejI7DH3Uc/view?usp=share_link}{\footnotesize  \faIcon{link}}.}
\resumeHeadingSkillEnd
% \hfill \textit{\footnotesize{*To be completed by Dec. 2022}}

% \vspace{1em}
%-----------RESPONSIBILITY-----------------
\section{Positions of Responsibility}
\resumeSubHeadingListStart
\resumePOR{Teaching Assistant} % Position
    {for the course \textbf{Data Science in Practices}, Dept. of Data Science and \\Engineering.
    Examination conduction, assignment preparation, answer sheet evaluation \\for a class of 120 students.} %Club,Event
    {Aug - Nov 2022} %Tenure Period
\resumePOR{Volunteer at NGO} % Position
    {\textbf{Swadhin Educational and Charitable Trust}, Sambalpur, Odisha. \\
    Organised multiple food and clothes distribution campaign for daily wage workers,\\
    Sanitizers and masks distribution for needy ones during COVID-19.} %Club,Event
    {2019 - 2021} %Tenure Period
\resumePOR{Organising Committee} % Position
    {Conference for \textbf{National Assembly of Researchers in Physics} \\(NARIPHY), IISER Bhopal.} %Club,Event
    {Aug 2022} %Tenure Period
\resumePOR{Technical Head cum Core Commitee} % Position
    {Annual cultural fest, Enthuzia, IISER Bhopal.} %Club,Event
    {2020 - 2021} %Tenure Period
\resumePOR{Club Coordinator} % Position
    {Chess Club, IISER Bhopal.} %Club,Event
    {2020 - 2021} %Tenure Period
\resumePOR{Editorial Board} % Position
    {Chrysalis Science Magazine, IISER Bhopal.} %Club,Event
    {2019 - 2020} %Tenure Period
\resumeSubHeadingListEnd


\vspace{1 mm}
%-----------ACHIEVEMENTS-----------------
\section{Achievements}
\resumeSubHeadingListStart
\resumePOR{Gold Medal} % Award
    {Inter-IISER Sports Meet (IISM) - Football.} % Event
    {2022} %Event Year
    
\resumePOR{Gold Medal} % Award
    {International Genetically Engineered Machine competition (iGEM).} % Event
    {2020} %Event Year

\resumePOR{Gold Medal} % Award
    {Inter-IISER Sports Meet (IISM) - Chess.} % Event
    {2018} %Event Year

\resumePOR{Gold, Silver, Bronze Medals} % Award
    {All India Kendriya Vidyalaya National Sports (Chess) Meet.} % Event
    {2010 - 2016} %Event Year

\resumePOR{Participant} % Award
    {National Junior Chess Championship, Lucknow.} % Event
    {2013} %Event Year

\resumeSubHeadingListEnd

\hspace*{-5mm}\rule{1.035\textwidth}{0.1mm}

%-------------------------------------------
\end{document}
